Global Climate and Atmosphere Composition of the Ultra-Hot Jupiter WASP-103\lowercase{b} from \HST\ and Spitzer Phase Curve Observations

### 2018-01-07 ms.tex
abstract

\author{Laura Kreidberg}
\affiliation{Harvard Society of Fellows\
78 Mt. Auburn St.\\
Cambridge, MA 02138, USA}
\affiliation{Harvard-Smithsonian Center for Astrophysics\
60 Garden St.\\
Cambridge, MA 02138}

@@

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/Wide Field Camera 3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux ranges from FIXME to FIXME at $1.1 - 4.5\,\mu$m.  The phase curves are symmetric and large amplitude, indicative of poor redistribution. We fit the phase curves with the SPIDERMAN package to determine the brightness distribution in the photosphere, and find the peak dayside temperature ranges from FIXME to FIXME depending on model.  We also generate phase-resolved spectra, which are consistent with blackbody models for the planet's emission at near-infrared wavelengths, but show strong emission features in the \Spitzer\ bands. We attribute these features to CO emission and a thermal inversion. The retrieved atmospheric composition is more metal-enriched than other hot Jupiters (FIXME). The carbon-to-oxygen ratio is consistent with solar composition. The absence of water features is due to BLAH. We compare the phase curves to general circulation models and find that atmospheric drag is required.  We also compare the spectra to brown dwarfs and young directly imaged companions and find that the water features are significantly diminished in amplitude. power of phase curve observations to elucidate the three-dimensional structure of exoplanet atmospheres.

inversion on the dayside but not on the nightside
\end{abstract}

@@

We calculated the planet-to-star flux $F_p/F_s$ in two different ways. First, we fit a sinusoid with a period equal to the planet's orbital period. The free parameters were the sine curve amplitude and phase offset. For the second approach, we used the \texttt{SPIDERMAN} package \citep{louden17} to model $F_p/F_s$. This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$. In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}.  For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang17}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).  In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.

@@

\section{Results}
\label{sec:results}
The fitted light curves are shown in Figure\,\ref{fig:phasecurves}. This figure shows results from the spherical harmonics model for the thermal phase variation and has instrument systematics removed.  Broadly speaking, the phase curves show large amplitude phase variation, ranging from 1.5 parts-per-thousand (ppt) in the WFC3 bandpass to 5 ppt in \Spitzer\ Channel 2.  The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5. In this section, we quantitatively characterize the phase curve shape, split the data into phase resolved spectra, evaluate different different temperature maps, and compare with previous observations of the dayside thermal emission spectrum.

@@

\subsection{Phase-Resolved Spectra}
We used the best-fit phase curves (with systematics removed) to generate phase-resolved emission spectra.  Since our model does not fit eclipse depth as a free parameter, we estimated the dayside emission spectrum as follows. We used \texttt{SPIDERMAN}'s eclipse\_depth method to calculate the average planet-to-star flux for the best-fit model during secondary eclipse.  To estimate uncertainties, we took the standard deviation of the residuals of the in-eclipse data points, then added this value in quadrature to the standard deviation of the residuals of the out-of-eclipse data.  This quadrature sum accounts for the uncertainty in the baseline flux. To account for red noise in the \Spitzer\ $3.6\,\mu$ light curve, we use the approach of \cite{pont06} to determine the red noise contribution on the timescale of the eclipse. We add the estimated red noise in quadrature, which increases the uncertainty on planet-to-star flux by a factor of $2.5$.

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag3}$ s. Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.}
\label{fig:spectra}
\end{figure*}

@@

\begin{deluxetable}{LLL}
	\tablecolumns{3}
	\tablewidth{0pt}
	\tablecaption{Phase-resolved Effective Temperature \label{table:teffs}}
	\tablehead{
	\colhead{Orbital Phase} & \colhead{$T_\mathrm{eff}$} & \colhead{$\chi^2_\nu$}}
		\startdata
		0.06 - 0.15 & 1919 \pm 40 & 0.6 \\
		0.15 - 0.25 & 2256 \pm 24 & 0.8 \\
		0.25 - 0.35 & 2651 \pm 17 & 1.2 \\
		0.35 - 0.44 & 2906 \pm 11 & 0.8 \\
		0.44 - 0.56 & 3013 \pm 8 & 1.6 \\
		0.56 - 0.65 & 2885 \pm 12 & 1.3 \\
		0.65 - 0.75 & 2636 \pm 16 & 0.9 \\
		0.75 - 0.85 & 2313 \pm 23 & 1.1 \\
		0.85 - 0.94 & 2027 \pm 36 & 0.5 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
	\end{deluxetable}

@@

To assess how well the GCM predictions reproduce the data, we calculated the amplitude and hot spot offset for all the models (listed in Table\,\ref{table:amps_offsets}). The observed hotspot offsets ($0.3 - 2.0$ degrees) are best reproduced by the $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$ models, which have small offsets due to slower wind speeds.  The nominal and metal-enhanced GCMs both have offsets that are too large (10-20 degrees). On the other hand, the drag models do not match the observed phase curve amplitudes (with values near unity, in contrast to the 0.8 - 0.9 that is observed). As shown in Figure\,\ref{fig:gcmcomparison}, the drag models predict the dayside planet-to-star flux fairly accurately, but underestimate the planet-to-star flux away from the substellar point. (\textbf{Vivien and others: how do we heat up the nightside to match the data better?})

@@

The GCMs also provide insight into what molecules are present in which parts of the atmosphere. As discussed in \S\,\ref{sec:composition}, water dissociation and H- opacity are needed to explain the dayside emission spectrum. Figure\,\ref{fig:gcmcomparison} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag3}$ GCM. The water abundance drops by $\sim10$ at the substellar point, and the H- opacity increases by $\sim100$.  By contrast, CO remains intact throughout the atmosphere.  Our observations are not precise enough to detect water features on the nightside of the planet (see \S\,\ref{sec:comparison}, but future high precision data may be sensitive to these features, and will help constrain the strength of horizontal transport in the atmosphere \citep{agundez14}.

@@

The main spectral feature over the wavelength range we consider is water. To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (F_{\lambda_1, \lambda_2} - F_{\lambda_3, \lambda_4})/F_{\lambda_1,\lambda_2}$, where $F_{\lambda_x, \lambda_y}$ is the weighted mean flux in a wavelength bin $x - y$. We calculated the water feature amplitude for two choices of wavelength bins. For the first, $A_1$, we considered data in and out of the water band, with $\lambda_{1,2,3,4} = 1.15, 1.3, 1.35, 1.5\,\mu$m. The ground-based direct imaging data doesn't span this entire wavelength, so we also define an amplitude $A_2$ with $\lambda_{1,2,3,4} = 1.2, 1.35, 1.5, 1.65\,\mu$m. The estimated amplitudes and uncertainties are listed in Table\,\ref{table:sources}.

For WASP-103b, $A_1$ is consistent with zero at all three orbital phases. The brown dwarfs have similar

\begin{deluxetable*}{llCCCC}
	\tablecolumns{6}
	\tablewidth{0pt}
	\tablecaption{Source Properties \label{table:sources}}
	\tablehead{
	\colhead{\,} & \colhead{Object} & \colhead{$T_\mathrm{eff}$} & \colhead{logg} & \colhead{H$_2$O A$_1$} & \colhead{H$_2$O A$_2$}}
		\startdata
		Hot Jupiter & W103b night & 1922 \pm 40 & 3.2 \pm 0.04 & 0.07 \pm 1.8\mathrm{e}-01 & -0.00 \pm 1.6\mathrm{e}-01 \\
		\, & W103b quadrature & 2408 \pm 20 & 3.2 \pm 0.04 & -0.14 \pm 7.8\mathrm{e}-02 & -0.01 \pm 6.7\mathrm{e}-02 \\
		\, & W103b dayside & 2982 \pm 10 & 3.2 \pm 0.04 & 0.04 \pm 1.4\mathrm{e}-02 & 0.15 \pm 1.2\mathrm{e}-02 \\
		Brown Dwarf & 2MASS J1320+0409 & 1875 \pm 70 & 5.19 \pm 0.16 & 0.21 \pm 6.3\mathrm{e}-04 & -0.06 \pm 5.0\mathrm{e}-04 \\
		\, & 2MASS J0428-2253 & 2429 \pm 80 & 5.22 \pm 0.09 & 0.16 \pm 1.2\mathrm{e}-04 & -0.03 \pm 1.0\mathrm{e}-04 \\
		\, & 2MASS J0003-2822 & 2889 \pm 80 & 5.18 \pm 0.04 & 0.26 \pm 1.3\mathrm{e}-04 & 0.10 \pm 1.1\mathrm{e}-04 \\
		Imaged Companion & CD-35 2722\tablenotemark{1} & 1800 \pm 100 & 4.5 \pm 0.5 & - & 0.15 \pm 1.0\mathrm{e}-05 \\
		\, & USco 1610-1913B\tablenotemark{2} & 2400 \pm 150 & - & 0.27 \pm 2.0\mathrm{e}-04 & 0.19 \pm 2.2\mathrm{e}-04 \\
		\, & TWA 22A\tablenotemark{3} & 3000 \pm 100 & 4.5 \pm 0.5 & - & 0.29 \pm 2.0\mathrm{e}-05 \\
		\enddata
	\tablenotetext{1}{\cite{wahhaj11}}
	\tablenotetext{2}{\cite{aller13}}
	\tablenotetext{3}{\cite{bonnefoy14}}
	\end{deluxetable*}

\section{Summary}
\label{sec:summary}
We observed thermal phase curves of the hot Jupiter WASP-103b measured with \HST/WFC3 time series spectroscopy ($1.15 - 1.65\,\mu$m) and \Spitzer/IRAC broadband photometry ($3.6$ and $4.6\,\mu$m bands).

\begin{itemize}
	\item{The phase curves have large amplitudes ($0.8 -0.9\times$ the secondary eclipse depth), and small offsets in peak brightness from the substellar point (consistent with zero degrees at all wavelengths). These characteristics indicate inefficient redistribution of heat to the nightside, as seen in other very hot Jupiters \citep{komacek17}.}
	\item{We fit the phase variation with the \texttt{spiderman} package \citep{louden17} to evaluate different models of the planets climate. A spherical harmonic temperature map generally provides the best fit to the data; however, all the maps produce reasonable fits ($\chi^2_\nu$ near unity), and there are large differences in temperature between them ($> 1000$ K). Breaking the degeneracy between different climate maps will require higher precision phase curves and/or secondary eclipse mapping \citep[e.g.][]{dewit12}.}
	\item{We calculated phase-resolved spectra in ten orbital phase bins. The \HST/WFC3 spectra are consistent with  blackbody emission from the planet at all orbital phases. The best fit effective temperatures ranges from 1920 K (phase $\phi = 0.1$) to 3010 K on the dayside. We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside, (2) additional near-IR opacity from H-, TiO/VO and FeH, (3) a small temperature gradient at the pressure levels probed by the data.  The \Spitzer\ data are \emph{not} consistent with a blackbody: there is an infrared emission feature at phases where the substellar point is visible ($\phi = 0.2 - 0.7$), which transitions to an absorption feature on the nightside ($\phi = -0.1 - 0.1$). We attribute these features to CO and changing thermal structure from the dayside to the nightside.}
	\item{We characterized the composition with a 1D grid-based retrieval that assumes thermochemical and radiative-convective equilibrium. The atmosphere is moderately metal-enriched ($23^{+29}_{-13}\times$ solar; and $>1\times$ solar at $3\,\sigma$ confidence). This value is somewhat higher than what is observed for other gas giants and predicted by models \citep[e.g.][]{wong04, kreidberg14b, mordasini16}, and may be indicative of intrinsic scatter in the relationship between atmospheric metallicity and planet mass. However, the metallicity is strongly sensitive to the $4.5\,\mu$m \Spitzer\ eclipse depth, and additional observations would be useful in confirming the metal enhancement.  In addition to metallicity, we also infer an upper limit on the carbon-to-oxygen ratio of 0.9 ($3\,\sigma$ confidence). This estimate agrees with expectations from planet formation models that pollution from water ice in planetesimals leads to $\mathrm{C/O} < 1$ in gas giant atmospheres \citep{mordasini16, espinoza17}. The best fit temperature pressure profile has a thermal inversion from $\sim10^{-2} - 10^{-3}$ bars due to TiO/VO absorption at high altitudes.} 
	\item{We ran several 3D GCMs to compare to the data, including a nominal model with a cloud-free, solar composition, a metal-enriched model ([Fe/H] = 0.5), and two models with Lorentz drag. The GCMs with Lorentz drag have slower wind speeds and provide the best match to the data small hotspot offsets that are observed, but they underpredict the palent's nightside flux.}
	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside0, 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature. Both the brown dwarfs and imaged companions show evidence for water features, as defined by FIXME spectral index. Cite Beatty }
\end{itemize}

>>>>

\author{Laura Kreidberg}
\affiliation{Harvard-Smithsonian Center for Astrophysics\
60 Garden St.\\
Cambridge, MA 02138}
\affiliation{Harvard Society of Fellows}

@@

\begin{abstract}
	We present thermal phase curve measurements for the hot Jupiter WASP-103b observed with \emph{Hubble}/WFC3 and \emph{Spitzer}/IRAC. The dayside planet-to-star flux is $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in bandpasses centered at $1.4$, $3.6$, and $4.5\mu$m, respectively.  The phase curves have large amplitudes and negligible hotspot offsets, indicative of poor heat redistribution to the nightside. We fit the phase variation with a range of climate maps and find they all provide reasonable fits to the data, but have large degeneracies in temperature (up to 1000 K for a given latitude/longitude). The phase-resolved spectra are consistent with blackbodies in the WFC3 bandpass, with effective temperatures ranging from 2000 K on the nightside to 3000 K on the dayside. However, the dayside spectrum has a strong feature in the \Spitzer\ bands, which we attribute to CO emission and a thermal inversion.  The emission feature is not present on the nightside, indicating changing thermal structure with longitude. We retrieved the atmospheric composition with a 1D thermochemical equilibrium model and found the composition is moderately metal-enriched ($\mathrm{[Fe/H]} =  23^{+29}_{-13}\times$ solar), and the carbon-to-oxygen ratio is below 0.9 at $3\,\sigma$ confidence. In contrast to other hot Jupiters, we do not detect significant water absorption, which we attribute to H$_2$O dissociation and additional opacity from H- and TiO/VO.  We compare the phase curves to 3D general circulation models and find that atmospheric drag is required to explain the small hotspot offsets, but that these models overpredict the phase curve amplitude.  We also compare the WASP-103b spectra to brown dwarfs and young directly imaged companions and find they have significantly larger water features, indicating that surface gravity and irradiation environment play an important role in shaping the spectra of hot Jupiters. 
\end{abstract}

@@

We calculated the planet-to-star flux $F_p/F_s$ in two different ways. First, we fit a sinusoid with a period equal to the planet's orbital period. The free parameters were the sine curve amplitude and phase offset. For the second approach, we used the \texttt{spiderman} package \citep{louden17} to model $F_p/F_s$. This package allows users to input a climate map (temperature or brightness as a function of latitude and longitude), and generate the corresponding flux ratio for an observation at time $t$. In our fit, we calculated the stellar flux with a PHOENIX model \citep{husser13} interpolated to an effective temperature of $6110\,\mathrm{K}$ \citep{gillon14}.  For the planet flux, we tested three different maps: a two-temperature map, with a uniform dayside temperature $T_d$ and a uniform nightside temperature $T_n$; a map generated with spherical harmonics; and the physically-motivated kinematic model from \cite{zhang17}, which has just three free parameters (the nightside temperature $T_n$, the change in temperature from day-to-night side $\Delta_T$, and the ratio of radiative to advective timescales $\xi$).  In all cases, we assumed that the planet is tidally locked, such that each orbital revolution corresponds to one complete rotation on its spin axis.

@@

\section{Results}
\label{sec:results}
The fitted light curves are shown in Figure\,\ref{fig:phasecurves}. This figure shows results from the spherical harmonics model for the thermal phase variation and has instrument systematics removed.  Broadly speaking, the phase curves show large dayside planet-to-star flux values, ranging from $0.151\pm0.015\%$, $0.446\pm0.38\%$, and $0.569\pm0.014\%$ in the WFC3 white light curve, and \Spitzer\ $3.6$, and $4.5\mu$m bandpasses, respectively.  The planet flux changes significantly with orbital phase in all three of the data sets, suggesting a strong gradient from dayside to nightside temperature, and peak brightness occurs near phase 0.5. In this section, we quantitatively characterize the phase curve shape, split the data into phase resolved spectra, evaluate different different temperature maps, and compare with previous observations of the dayside thermal emission spectrum.

@@

\subsection{Phase-Resolved Spectra}
We used the best-fit phase curves (with systematics removed) to generate phase-resolved emission spectra.  Since our model does not fit eclipse depth as a free parameter, we estimated the dayside emission spectrum as follows. We used \texttt{spiderman}'s eclipse\_depth method to calculate the average planet-to-star flux for the best-fit model during secondary eclipse.  To estimate uncertainties, we took the standard deviation of the residuals of the in-eclipse data points, then added this value in quadrature to the standard deviation of the residuals of the out-of-eclipse data.  This quadrature sum accounts for the uncertainty in the baseline flux. To account for red noise in the \Spitzer\ $3.6\,\mu$m light curve, we use the approach of \cite{pont06} to determine the red noise contribution on the timescale of the eclipse. We add the estimated red noise in quadrature, which increases the uncertainty on planet-to-star flux by a factor of $2.5$.

@@

\begin{figure*}
\includegraphics[width = 1.0\textwidth]{Figures/emission_spectra.pdf}
\caption{Phase-resolved emission spectra (points) compared to the best fit blackbody (blue line) and the GCM with $\tau_\mathrm{drag3}$. Phases $\phi = 0.5$ and $0.0$ are centered on the substellar and anti-stellar points, respectively.}
\label{fig:spectra}
\end{figure*}

@@

\begin{deluxetable}{LLL}
	\tablecolumns{3}
	\tablewidth{0pt}
	\tablecaption{Phase-resolved Effective Temperature \label{table:teffs}}
	\tablehead{
	\colhead{Orbital Phase} & \colhead{$T_\mathrm{eff}$ (K)} & \colhead{$\chi^2_\nu$}}
		\startdata
		0.06 - 0.15 & 1919 \pm 40 & 0.6 \\
		0.15 - 0.25 & 2256 \pm 24 & 0.8 \\
		0.25 - 0.35 & 2651 \pm 17 & 1.2 \\
		0.35 - 0.44 & 2906 \pm 11 & 0.8 \\
		0.44 - 0.56 & 3013 \pm 8 & 1.6 \\
		0.56 - 0.65 & 2885 \pm 12 & 1.3 \\
		0.65 - 0.75 & 2636 \pm 16 & 0.9 \\
		0.75 - 0.85 & 2313 \pm 23 & 1.1 \\
		0.85 - 0.94 & 2027 \pm 36 & 0.5 \\
		\enddata
		\vspace{-0.8cm}
		\tablecomments{comments}
	\end{deluxetable}

@@

To assess how well the GCM predictions reproduce the data, we calculated the amplitude and hot spot offset for all the models (listed in Table\,\ref{table:amps_offsets}). The observed hotspot offsets ($0.3 - 2.0$ degrees) are best reproduced by the $\tau_\mathrm{drag3}$ and $\tau_\mathrm{drag4}$ models, which have small offsets due to slower wind speeds.  The nominal and metal-enhanced GCMs both have offsets that are too large (10-20 degrees). On the other hand, the phase curve amplitudes are better matched by the nominal GCM than either of the drag models. The most precise observed amplitude is $0.91\pm0.02$ (in the WFC3 bandpass), which is significantly smaller than the amplitudes predicted by the drag models (0.97, 0.99). As shown in Figure\,\ref{fig:gcmcomparison}, this large amplitude causes the drag models to underestimate the planet-to-star flux away from the substellar point. (\textbf{Vivien and others: how do we heat up the nightside to match the data better?})

@@

The GCMs also provide insight into what molecules are present in which parts of the atmosphere. As discussed in \S\,\ref{sec:composition}, water dissociation and H- opacity are needed to explain the dayside emission spectrum. Figure\,\ref{fig:gcmcomparison} shows the photospheric abundances of H$_2$O and H- compared to the predicted temperature for the $\tau_\mathrm{drag3}$ GCM. The water abundance drops by $\sim10$ at the substellar point, and the H- opacity increases by $\sim100$.  By contrast, CO remains intact throughout the atmosphere.  Our observations are not precise enough to detect water features on the nightside of the planet (see \S\,\ref{sec:comparison}), but future high precision data may be sensitive to these features, and will help constrain the strength of horizontal transport in the atmosphere \citep{agundez14}.

@@

We compared the spectra over the wavelength range $1.1 - 1.7\mu$m. The dominant opacity source over this range is water, which has a forest of absorption lines near 1.4\,$\mu$m. Spectra for the brown dwarfs and imaged companions have noticeable features in the water band, whereas WASP-103b does not. To quantitatively compare the water feature amplitude for different objects, we define an amplitude $A = (F_{1,2} - F_{3,4})/F_{1,2}$, where $F_{1,2}$ is the weighted mean flux in a wavelength bin $\lambda_1 - \lambda_2$. We calculated the water feature amplitude for two choices of wavelength bins. For the first, $A_1$, we considered data in and out of the water band, with $\lambda_{1,2,3,4} = 1.15, 1.3, 1.35, 1.5\,\mu$m. The ground-based direct imaging data doesn't span this entire wavelength range, so we also define an amplitude $A_2$ with $\lambda_{1,2,3,4} = 1.2, 1.35, 1.5, 1.65\,\mu$m. The estimated amplitudes and uncertainties are listed in Table\,\ref{table:sources}.

The $A_1$ and $A_2$ values are significantly lower for WASP-103b at dayside and quadrature than for brown dwarfs and imaged companions of similar temperature. WASP-103b typically has $A_1$ and $A_2$ consistent with zero, indicating no water absorption (in agreement with the analysis in \S\,\ref{sec:results} that showed water is depleted in the photosphere). By contrast, the brown dwarfs and young companions have significant water features, with drops in flux of about 20\% in the water band. This is not surprising: stars in the temperature range $2000 - 3000\,\mathrm{K}$ are well known to have prominent water features \citep{kirkpatrick93}.  Based on the grid retrieval of WASP-103b's atmospheric composition, there are two reasons WASP-103b would exhibit different behavior at the same temperature. First, the atmosphere of WASP-103b is irradiated from above rather than below, leading to a more isothermal temperature profile and weaking spectral features. In addition, WASP-103b also has much lower surface gravity (log$g$ = 3.2 versus 4-5 for stars), which pushes the photosphere to lower pressures, where water dissociates more readily (\textbf{Mike: need a reference for this}). These factors are not relevant on the nightside, and WASP-103b may have water absorption features there; however, the current data are not precise enough to distinguish between a blackbody spectrum versus water features like those seen in the other objects.

\begin{deluxetable*}{llCCCC}
	\tablecolumns{6}
	\tablewidth{0pt}
	\tablecaption{Source Properties \label{table:sources}}
	\tablehead{
	\colhead{\,} & \colhead{Object} & \colhead{$T_\mathrm{eff}$ (K)} & \colhead{log\,$g$ (cgs)} & \colhead{H$_2$O A$_1$} & \colhead{H$_2$O A$_2$}}
		\startdata
		Hot Jupiter & W103b night & 1922 \pm 40 & 3.2 \pm 0.04 & 0.07 \pm 1.8\mathrm{e}-01 & -0.00 \pm 1.6\mathrm{e}-01 \\
		\, & W103b quadrature & 2408 \pm 20 & 3.2 \pm 0.04 & -0.14 \pm 7.8\mathrm{e}-02 & -0.01 \pm 6.7\mathrm{e}-02 \\
		\, & W103b dayside & 2982 \pm 10 & 3.2 \pm 0.04 & 0.04 \pm 1.4\mathrm{e}-02 & 0.15 \pm 1.2\mathrm{e}-02 \\
		Brown Dwarf & 2MASS J1320+0409 & 1875 \pm 70 & 5.19 \pm 0.16 & 0.21 \pm 6.3\mathrm{e}-04 & -0.06 \pm 5.0\mathrm{e}-04 \\
		\, & 2MASS J0428-2253 & 2429 \pm 80 & 5.22 \pm 0.09 & 0.16 \pm 1.2\mathrm{e}-04 & -0.03 \pm 1.0\mathrm{e}-04 \\
		\, & 2MASS J0003-2822 & 2889 \pm 80 & 5.18 \pm 0.04 & 0.26 \pm 1.3\mathrm{e}-04 & 0.10 \pm 1.1\mathrm{e}-04 \\
		Imaged Companion & CD-35 2722\tablenotemark{1} & 1800 \pm 100 & 4.5 \pm 0.5 & - & 0.15 \pm 1.0\mathrm{e}-05 \\
		\, & USco 1610-1913B\tablenotemark{2} & 2400 \pm 150 & - & 0.27 \pm 2.0\mathrm{e}-04 & 0.19 \pm 2.2\mathrm{e}-04 \\
		\, & TWA 22A\tablenotemark{3} & 3000 \pm 100 & 4.5 \pm 0.5 & - & 0.29 \pm 2.0\mathrm{e}-05 \\
		\enddata
	\tablenotetext{1}{\cite{wahhaj11}}
	\tablenotetext{2}{\cite{aller13}}
	\tablenotetext{3}{\cite{bonnefoy14}}
	\end{deluxetable*}

\section{Summary}
\label{sec:summary}
We observed thermal phase curves of the hot Jupiter WASP-103b measured with \HST/WFC3 time series spectroscopy ($1.15 - 1.65\,\mu$m) and \Spitzer/IRAC broadband photometry ($3.6$ and $4.6\,\mu$m bands). Here we summarize our conclusions about the atmosphere based on these measurements.

\begin{itemize}
	\item{The dayside secondary eclipse depths are FIXME, implying a dayside effective temperature of FIXME, making WASP-103b among the hottest hot Jupiters ever observed.}
	\item{The phase curves have large amplitudes ($0.8 -0.9\times$ the secondary eclipse depth), and small offsets in peak brightness from the substellar point (consistent with zero degrees at all wavelengths). These characteristics indicate inefficient redistribution of heat to the nightside, as seen in other very hot Jupiters \citep{komacek17}.}
	\item{We fit the phase variation with the \texttt{spiderman} package \citep{louden17} to evaluate different models of the planet's climate, including a two-temperature map, a physically-motivated kinematic map, and spherical harmonics. The spherical harmonic temperature map generally provides the best fit to the data; however, all the maps produce reasonable fits ($\chi^2_\nu$ near unity), and there are large differences in temperature between them (up to 1000 K at a given latitude/longitude). Breaking the degeneracy between different climate maps will require higher precision phase curves and/or secondary eclipse mapping \citep[e.g.][]{dewit12}.}
	\item{We calculated phase-resolved spectra in ten orbital phase bins. The \HST/WFC3 spectra are consistent with  blackbody emission from the planet at all orbital phases. The best fit effective temperatures ranges from 1920 K (phase $\phi = 0.1$) to 3010 K on the dayside. We attribute the absence of water features at WFC3 wavelengths to (1) H$_2$O dissociation on the dayside, (2) additional near-IR opacity from H-, TiO/VO and FeH, (3) a small temperature gradient at the pressure levels probed by the data.  The \Spitzer\ data are \emph{not} consistent with a blackbody: there is an infrared emission feature at phases where the substellar point is visible ($\phi = 0.2 - 0.7$), which transitions to an absorption feature on the nightside ($\phi = -0.1 - 0.1$). We attribute these features to CO absorption and changing thermal structure from the dayside to the nightside.}
	\item{We characterized the composition with a 1D grid-based retrieval that assumes thermochemical and radiative-convective equilibrium. The atmosphere is moderately metal-enriched ($23^{+29}_{-13}\times$ solar; and $>1\times$ solar at $3\,\sigma$ confidence). This value is somewhat higher than what is observed for other gas giants and predicted by models \citep[e.g.][]{wong04, kreidberg14b, mordasini16}, and may be indicative of intrinsic scatter in the relationship between atmospheric metallicity and planet mass. However, the metallicity is strongly sensitive to the $4.5\,\mu$m \Spitzer\ eclipse depth, and additional observations would be useful in confirming the metal enhancement.  In addition to metallicity, we also infer an upper limit on the carbon-to-oxygen ratio of 0.9 ($3\,\sigma$ confidence). This estimate agrees with expectations from planet formation models that pollution from water ice in planetesimals leads to $\mathrm{C/O} < 1$ in gas giant atmospheres \citep{mordasini16, espinoza17}. The best fit temperature pressure profile has a thermal inversion from $\sim10^{-2} - 10^{-3}$ bars due to TiO/VO absorption at high altitudes.} 
	\item{We ran several 3D GCMs to compare to the data, including a nominal model with a cloud-free, solar composition, a metal-enriched model ([Fe/H] = 0.5), and two models with Lorentz drag. The GCMs with Lorentz drag have slower wind speeds and provide the best match to the data small hotspot offsets that are observed, but they underpredict the planet's nightside flux.}
	\item{We compared the spectra of WASP-103b at phases 0.5 (dayside), 0.25 (quadrature), and 0.1 (nightside) to brown dwarfs and directly imaged companions of similar temperature. We quantify the strength of the water feature and find that both brown dwarfs and imaged companions show evidence for water absorption at $1.4\,\mu$m, whereas WASP-103b does not. We attribute the difference to two factors: WASP-103b's irradiation environment, which changes the temperature pressure profile, and its low surface gravity, which pushes the photosphere to higher altitudes where water dissociates more easily.}
\end{itemize}
